---
title: "Art Grants in LA"
author: "Luke Wolcott"
date: "December 17, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE)
```

---

### Week 3 assignment for JHU: Developing Data Products

#### Instructions:

Create a web page presentation using R Markdown that features a plot created with Plotly. Host your webpage on either GitHub Pages, RPubs, or NeoCities. Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly. 

---

### Dataset

The data come from the following website.

```https://data.lacounty.gov/Arts-and-Culture/Organizational-Grants-for-Arts-Services/73tm-r9gy```

It contains information about art grants given through the Organizational Grant Program of the Los Angeles County Arts Commission, over the three application years of 2014-15, 2015-16, and 2016-17.  This was accessed on December 17th 2016, and downloaded as a 92 kb CSV file into the working directory.  See the Appendix for code.


```{r, echo=FALSE}
data <- read.csv("Organizational_Grants_for_Arts_Services.csv")
library(plotly)
library(dplyr)
```


```{r, echo=FALSE}
data$Grant.Award <- sub('.','',as.character(data$Grant.Award))
data$Grant.Award <- as.numeric(data$Grant.Award)
for (i in 1:568)
      if (data[i,2] == "Arts Service/")
            data[i,2] <- as.factor("Arts Service ")
```


### A. Spread of money awarded, by discipline

```{r, echo=FALSE}
plot_ly(data, y = ~Grant.Award, color = ~Discipline, type = "box")
```

### B. Spread of money awarded, by application year

```{r, echo=FALSE}
plot_ly(data, y = ~Grant.Award, color = ~Application.Year, type="box")
```

### C. Number of grants awarded versus total amount awarded, by discipline

```{r, echo=FALSE}
by_disc <- group_by(data, Discipline)
d <-summarize(by_disc, Total.Amount.Awarded = sum(Grant.Award), Number.Awarded = length(Grant.Award))
plot_ly(d, x=~Number.Awarded, y=~Total.Amount.Awarded, mode="markers", text = ~Discipline)
```

### Appendix: Code

```{r, eval=FALSE}
# Data and cleaning
data <- read.csv("Organizational_Grants_for_Arts_Services.csv")
library(plotly)
library(dplyr)

# Convert the grant award amount to a numeric that is easy to work with.  
# Fix a typo in the name of one of the disciplines.
data$Grant.Award <- sub('.','',as.character(data$Grant.Award))
data$Grant.Award <- as.numeric(data$Grant.Award)
for (i in 1:568)
      if (data[i,2] == "Arts Service/")
            data[i,2] <- as.factor("Arts Service ")

# A. Spread of money awarded, by discipline
plot_ly(data, y = ~Grant.Award, color = ~Discipline, type = "box")

# B. Spread of money awarded, by application year
plot_ly(data, y = ~Grant.Award, color = ~Application.Year, type="box")

# C. Number of grants awarded versus total amount awarded, by discipline
by_disc <- group_by(data, Discipline)
d <-summarize(by_disc, Total.Amount.Awarded = sum(Grant.Award), Number.Awarded = length(Grant.Award))
plot_ly(d, x=~Number.Awarded, y=~Total.Amount.Awarded, mode="markers", text = ~Discipline)
```

---
