---
title: "LA County Crimes on 10/02/2016"
author: "Luke Wolcott"
date: "December 16, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE)
```

----

### Week 2 assignment for JHU: Developing Data Products

#### Instructions:

Create a web page using R Markdown that features a map created with Leaflet.

----

### Dataset and cleaning

The data come from the following website.

```https://data.lacounty.gov/Criminal/LA-SHERIFF-CRIMES-LAST-12-MONTHS/ca5f-5zzs```

The dataset contains information about crimes in Los Angeles County in the last twelve months.  This was accessed on December 16th 2016, and downloaded as a 51 mb CSV file into the working directory.


```{r, cache=TRUE}
data <- read.csv("LA_SHERIFF__CRIMES_-_LAST_12_MONTHS.csv")
```

We'll subset for the crimes that happened on October 2nd 2016, which is Gandhi's birthday (why not?).  The first 27 entries have NAs for latitude and longitude, so we remove them.  We're interested in the crime category description, latitude, and longitude, so we'll subset for those columns.

```{r}
data$CRIME_DATE <- strptime(data$CRIME_DATE, "%m / %d / %Y %I : %M : %S %p")
d <- subset(data, (data$CRIME_DATE)$yday == 275)
d <- d[-c(1:27), c(1,4,12,13)]
names(d) <- c("CRIME_DATE", "popup", "lat", "lng")
dim(d)
```


### Map

Here's the map.  Zooming in and clicking on thumbnails will tell you the "crime category description".


```{r}
library(leaflet)
map <- d %>% leaflet() %>% addTiles %>% addMarkers(popup=d$popup,clusterOptions = markerClusterOptions())
map
```





---


